Network Data Collection for Artifical Intelligence

### 2020-02-24 paper2/paper2.tex
Separate multiple citations by space instead of comma

Other methods which can be used for that purpose are based on association rule mining (ARM) \cite{moustafa2015}, sequential forward selection (SFS) \cite{dehghani2010, xu2015}, or the T-test \cite{sopuru2019},

@@

Another aspect which has been examined is the stability of features in terms of time (year 2000/2001 vs. 2008) and location (Internet core vs. Internet edge). In this regard, the packet size can be considered a stable feature \cite{este2009}. The suitability of features also depends on the type of network which is analyzed. For example, industrial control system networks are relatively static regarding IP address and port allocation, protocols and settings used, and number of connections, therefore features based on these attributes may provide good results in that particular environment \cite{mantere2013}.

@@

A common approach is to group packets into flows, and then calculate statistical features based on these flows. Generally, a flow is a group of packets with the same source and destination IP addresses and ports, as well as protocol \cite{brownlee1998}. However, a flow can also be terminated by a TCP FIN packet or a timeout \cite{Ids2018}. Statistical features of network flows include the following:
\begin{itemize}
	\item Flow duration \cite{Nb2015, Ids2018}
	\item Time between two flows or packets \cite{Ids2018}
	\item Time between SYN and SYN/ACK, and between SYN/ACK and ACK packets during TCP connection setup \cite{Nb2015}
	\item Active time before a flow becomes idle and vice versa \cite{Ids2018}
	\item Jitter \cite{Nb2015}
	\item Number of packets in total, with at least 1 byte of payload, or with certain protocol flags \cite{Ids2018, waizumi2007, celik2015}
	\item Number of fragmented packets \cite{waizumi2007}
	\item Number of retransmitted or dropped packets \cite{Nb2015}
	\item Size of packets, payload, headers or segments \cite{Ids2018, celik2015}
	\item Number of bytes/packets transferred per second, in bulk, or in the initial TCP window \cite{Ids2018, celik2015}
	\item Number of RTT samples \cite{celik2015}
	\item Time to live value \cite{Nb2015}
	\item TCP window advertisement value \cite{Nb2015}
	\item TCP base sequence number \cite{Nb2015}
	\item Ratio between download and upload \cite{Ids2018}
	\item Ratio between maximum and minimum packet size \cite{celik2015}
	\item Number of flows with the current flow's IP address or port number \cite{waizumi2007, Nb2015}
\end{itemize}
Most of these features can be derived by statistical calculations such as total, minimum, maximum, mean, median, standard deviation, variance, skewness and kurtosis \cite{Ids2018, celik2015, xu2015}. Also, the features can be extracted from bidirectional flows, or separately for forward and backward directions \cite{Ids2018}.

The open-source Java software CICFlowMeter can be used to extract features of network flows (which end either by TCP FIN packet, or a configurable timeout) from pcap files. It allows to select from a list of available features, but can also be extended to support new features \cite{cicflowmeter}, and has therefore been used in various applications \cite{Ids2018, lashkari2017, sopuru2019}.

@@

In addition to the feature vectors, datasets to be used for supervised learning need to include labels. For the purpose of intrusion detection, each record (e.g., network flow) has to be labelled  binary as benign or malicious traffic, or nominally to distinguish between certain attack types. For example, the UNSW-NB15 dataset defines a binary label (0 for normal and 1 for attack) and a nominal label ("Normal" for benign traffic and "Fuzzers", "Analysis", "Backdoors", "DoS", "Exploits", "Generic", "Reconnaissance", "Shellcode" or "Worms" for the various attack types) \cite{Nb2015}. For some applications, there may also be a nominal label for benign traffic (e.g., browsing, chat, mail, P2P, streaming, VoIP) \cite{lashkari2017, bagui2017}.

>>>>

Other methods which can be used for that purpose are based on association rule mining (ARM) \cite{moustafa2015}, sequential forward selection (SFS) \cite{dehghani2010} \cite{xu2015}, or the T-test \cite{sopuru2019},

@@

Another aspect which has been examined is the stability of features in terms of time (year 2000/2001 vs. 2008) and location (Internet core vs. Internet edge). In this regard, the packet size can be considered as stable feature \cite{este2009}. The suitability of features also depends on the type of network which is analyzed. For example, industrial control system networks are relatively static regarding IP address and port allocation, protocols and settings used, and number of connections, therefore features based on these attributes may provide good results in that particular environment \cite{mantere2013}.

@@

A common approach is to group packets into flows, and then calculate statistical features based on these flows. Generally, a flow is a group of packets with the same source and destination IP addresses and ports, as well as protocol \cite{brownlee1998}. However, a flow can also be terminated by a TCP FIN packet or a timeout \cite{Ids2018}. Statistical features of network flows include the following:
\begin{itemize}
	\item Flow duration \cite{Nb2015} \cite{Ids2018}
	\item Time between two flows or packets \cite{Ids2018}
	\item Time between SYN and SYN/ACK, and between SYN/ACK and ACK packets during TCP connection setup \cite{Nb2015}
	\item Active time before a flow becomes idle and vice versa \cite{Ids2018}
	\item Jitter \cite{Nb2015}
	\item Number of packets in total, with at least 1 byte of payload, or with certain protocol flags \cite{Ids2018} \cite{waizumi2007} \cite{celik2015}
	\item Number of fragmented packets \cite{waizumi2007}
	\item Number of retransmitted or dropped packets \cite{Nb2015}
	\item Size of packets, payload, headers or segments \cite{Ids2018} \cite{celik2015}
	\item Number of bytes/packets transferred per second, in bulk, or in the initial TCP window \cite{Ids2018} \cite{celik2015}
	\item Number of RTT samples \cite{celik2015}
	\item Time to live value \cite{Nb2015}
	\item TCP window advertisement value \cite{Nb2015}
	\item TCP base sequence number \cite{Nb2015}
	\item Ratio between download and upload \cite{Ids2018}
	\item Ratio between maximum and minimum packet size \cite{celik2015}
	\item Number of flows with the current flow's IP address or port number \cite{waizumi2007} \cite{Nb2015}
\end{itemize}
Most of these features can be derived by statistical calculations such as total, minimum, maximum, mean, median, standard deviation, variance, skewness and kurtosis \cite{Ids2018} \cite{celik2015, xu2015}. Also, the features can be extracted from bidirectional flows, or separately for forward and backward directions \cite{Ids2018}.

The open-source Java software CICFlowMeter can be used to extract features of network flows (which end either by TCP FIN packet, or a configurable timeout) from pcap files. It allows to select from a list of available features, but can also be extended to support new features \cite{cicflowmeter}, and has therefore been used in various applications \cite{Ids2018} \cite{lashkari2017} \cite{sopuru2019}.

@@

In addition to the feature vectors, datasets to be used for supervised learning need to include labels. For the purpose of intrusion detection, each record (e.g., network flow) has to be labelled  binary as benign or malicious traffic, or nominally to distinguish between certain attack types. For example, the UNSW-NB15 dataset defines a binary label (0 for normal and 1 for attack) and a nominal label ("Normal" for benign traffic and "Fuzzers", "Analysis", "Backdoors", "DoS", "Exploits", "Generic", "Reconnaissance", "Shellcode" or "Worms" for the various attack types) \cite{Nb2015}. For some applications, there may also be a nominal label for benign traffic (e.g., browsing, chat, mail, P2P, streaming, VoIP) \cite{lashkari2017} \cite{bagui2017}.
